Where Do Events Come From?

### 2018-08-03 paper.tex
...

- excel define formulas for input but not the input itself

output -> input

the environment sits
    inverse
    reacts to output and generates inputs

remain idle and react to the occurrence of events

@@

The \code{par/or}, which stands for \emph{parallel-or}, is a lexical
composition that terminates as soon as one of the trails terminates, but which
also automatically finalizes the other trail(s).
%
In the example, when the button is pressed, not only the toggling loop will be
aborted, but the \code{finalize} clause will turn the LED off unconditionally,
since its enclosing block goes out of scope.

@@

\subsection{Interrupt Service Routines}
\label{sec.isrs}

@@

The example in Listing~\ref{lst.adc} illustrates the use of a lexically-scoped
driver for the A/D converter.
Note that the driver (ln~1--14) and application (ln~16--27) are actually in
separate files.
%
The application is a typical periodic sensor sampling loop, but which
designates an explicit \code{do--end} scope to execute the driver (ln~21) and
use it (ln~22--23).
%
The driver specifies a finalization code (ln~6--12) which executes
unconditionally whenever it goes out of scope (ln~24).
This code completely disables all A/D functionality, saving energy.
%
As discussed for Listing~\ref{lst.ceu}, finalizers also execute due to
\code{par/or} termination (or other abortion mechanisms of \CEU).
%
Note that the driver interface (ln~3--4) is visible only inside the block and
thus cannot be inadvertently used outside it.

>>>>

@@

The \code{par/or}, which stands for \emph{parallel-or}, is a lexical
composition that terminates as soon as one of the trails terminates, but which
also automatically aborts and finalizes the other trail(s).
%
In the example, when the button is pressed, not only the toggling loop will be
aborted, but the \code{finalize} clause will turn the LED off unconditionally,
since its enclosing block goes out of scope.
%
The \code{par/or} is regarded as an \emph{orthogonal preemption
primitive}~\cite{esterel.preemption} because the trails need not to be tweaked
in order to affect each other.

@@

\subsection{Lexically-Scoped Interrupt Service Routines}
\label{sec.isrs}

@@

The example in Listing~\ref{lst.adc} illustrates the use of a lexically-scoped
driver for the A/D converter.
Note that the driver (ln~1--14) and application (ln~16--27) are actually in
separate files.
%
The application is a typical periodic sensor sampling loop, but which
designates an explicit \code{do--end} scope to execute the driver (ln~21) and
use it (ln~22--23).
%
The driver specifies a finalization code (ln~6--12) which executes
unconditionally whenever it goes out of scope (ln~24).
This code completely disables all A/D functionality to save energy.
%
As discussed for Listing~\ref{lst.ceu}, the finalizer would also sensibly
execute due to a \code{par/or} termination enclosing the driver.
%
Note that the driver interface (ln~3--4) is visible only inside the block and
thus cannot be inadvertently used outside it.
